Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-26 paper/Draft.tex
Started drafting IR parts.first subsection done.

\section{Theories of Expectation Formation}

@@

\section{Empirical Results}

@@

\begin{table}[]\label{NullTestTable}
	\caption{Test of Rationality and Efficicency}
	\centering 
\begin{tabular}{llll}
	\hline 
	& SPF CPI          & SPF PCE          & SCE            \\
	\hline 
	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
	\hline 
	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
	& (0.017)          & (0.061)          & (0.019)        \\
	\hline 
	N                                   & 4697             & 1208             & 67380          \\
	\hline 
	\multicolumn{4}{l}{Test2: FE Depends on past information}                                  \\
	\hline 
	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
	& (0.020)          & (0.061)          & NA             \\
	Constant                            & -0.655***        & -0.777***        & NA             \\
	& (0.060)          & (0.116)          & NA             \\
	\hline 
	N                                   & 3429             & 1208             & NA             \\
	$R^2$                 & 0.0721           & 0.118            & NA             \\
	\hline 
	\multicolumn{4}{l}{Test3: FE of non-overlapping forecast horizons are serially correlated} \\
	\hline 
	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
	& (0.020)          & (0.035)          & NA             \\
	Constant                            & 0.145***         & 0.275***         & NA             \\
	& (0.021)          & (0.035)          & NA             \\
	\hline 
	N                                   & 3356             & 1208             & NA             \\
	$R^2$                   & 0.00591          & 0.00264          & NA             \\
	\hline 
	\multicolumn{4}{l}{Test4: Overlapping FE are only weakly serially correlated}                          \\
	\hline 
	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
	& (0.025)          & (0.037)          & (0.021)        \\
	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
	& (0.027)          & (0.048)          & (0.046)        \\
	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
	& (0.025)          & (0.038)          & (0.045)        \\
	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
	& (0.019)          & (0.026)          & (0.097)        \\
	\hline 
	N                                   & 2536             & 1004             & 2836           \\
	$R^2$                & 0.439            & 0.552            & 0.232    \\
	\hline      
\end{tabular}
\end{table}

@@

\subsection{Professional Forecasters as a Benchmark}

\subsubsection{Replicating \cite{coibion2012can}}

@@

\subsubsection{Additional Evidence from Uncertainty}

>>>>

\section{Theories of Expectation Formation}\label{theory}

@@

\section{Empirical Results}\label{empirical}

@@

\begin{table}[]\label{NullTestTable}
	\caption{Tests of Rationality and Efficicency using Forecast Errors}
	\centering 
\begin{tabular}{llll}
	\hline 
	& SPF CPI          & SPF PCE          & SCE            \\
	\hline 
	\multicolumn{4}{l}{Test 1: Bias}                                                           \\
	\hline 
	Constant                            & 0.122***         & 0.586***         & 2.220***       \\
	& (0.017)          & (0.061)          & (0.019)        \\
	\hline 
	N                                   & 4697             & 1208             & 67380          \\
	\hline 
	\multicolumn{4}{l}{Test 2: FE depends on past information}                                  \\
	\hline 
	Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
	& (0.020)          & (0.061)          & NA             \\
	Constant                            & -0.655***        & -0.777***        & NA             \\
	& (0.060)          & (0.116)          & NA             \\
	\hline 
	N                                   & 3429             & 1208             & NA             \\
	$R^2$                 & 0.0721           & 0.118            & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons are serially correlated} \\
	\hline 
	Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
	& (0.020)          & (0.035)          & NA             \\
	Constant                            & 0.145***         & 0.275***         & NA             \\
	& (0.021)          & (0.035)          & NA             \\
	\hline 
	N                                   & 3356             & 1208             & NA             \\
	$R^2$                   & 0.00591          & 0.00264          & NA             \\
	\hline 
	\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
	\hline 
	Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
	& (0.025)          & (0.037)          & (0.021)        \\
	Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
	& (0.027)          & (0.048)          & (0.046)        \\
	Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
	& (0.025)          & (0.038)          & (0.045)        \\
	Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
	& (0.019)          & (0.026)          & (0.097)        \\
	\hline 
	N                                   & 2536             & 1004             & 2836           \\
	$R^2$                & 0.439            & 0.552            & 0.232    \\
	\hline      
\end{tabular}
\end{table}

@@

\section{Responses of Expectations to Inflation Shocks }\label{IRShocks}

 \cite{Coibion2012can} explores the implications of expectation rigidity models using externally identified shocks to inflation.  Unlike the time series regressions that test null hypotheses of FIRE in previous section, this approach allows a more straightforward comparison between the emprical evidence from surveys and the theoriecal predictions illustrated in Figure \ref{ir_pop}. The difficulty of this approach lies in identifying a shock $\omega_t$ that is a pure innovation to inflation at time $t$.

In this paper I use three types of shocks: technology shock\cite{gali1999technology}, oil price shock\cite{hamilton1996happened} and monetary policy shocks \cite{laseen2011anticipated}. The first two are the same in \cite{Coibion2012can}. \footnote{ Another shock in \cite{Coibon2012can} is the news shock by \cite{barsky2011news}. This will be included in later version of the paper }

(1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts. \footnote{An recent alternative to long-run restriction approach is the ''max-share appraoch'' developed by \cite{francis2014flexible}. It is shown to have better small-sample properties. In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determiend horizon. The resutls using this shock will be included in a later version of the paper. For the replication purpose now, I stay with \cite{gali1999technology}}. The sample period used to identify the shock is 1949-2019, while the period where it enters my analysis is the same to the period of survey data: 2007-2019 for SPF and 2013-2019 for SCE.

(2) Oil price shock in each period is defined as the maximum of log change in crude oil prices over the past 1-year and 0. Therefore it is bounded zero.\footnote{The series of oil price is Spot Crude Oil Price: West Texas Intermediate (WTI).}

(3) Monetary policy shocks: target surprise and path surprise in the termiology of \cite{laseen2011anticipated}. Target surprise is defined as unexpected change in federal funds rate in a particular dates of FOMC meenting. It is the OLS residual of federal funds rate change in the past federal funds rate. The 2-year ahead path surprise is the regression residual of future implied federal funds rate on the target surprise. Depending on the frequency of the data being monthly or quarterly, I take the sum of all the changes within each period.

The reason for including monetary policy shocks, although it turns out to provide less robust evidence, is twofold. First, it is well known that the role of expectation in the working and implementation of monetary policy in the post criss period has been of a great relevance. Especially, around zero-lower-bound, the central banks have utilized nontraditional tools such as forward guidance which primarily works through influencing expectations of market agents.

In Figure \ref{Inflationshocks}, all four shocks plus the unexplained component of inflation are plotted in quarterly between 1985-2019. All shocks are normalized by its respective sample standard deviations.

\begin{figure}[h]\label{Inflationshocks}
	\centering
	\includegraphics[width=12cm]{figures/inf_shocksQ.png}
	\caption{ Shocks to Inflation}
\end{figure}

\subsection{Replicating \cite{coibion2012can}}

@@

\subsection{Additional Evidence from Uncertainty}
